ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-06 paper/paper.tex
update

We only applied stacking on task 2.
We tried two stacking method seperately
\begin{enumerate}
 \item 2-folds stacking split by two different time frame

@@

Since stacking index must be fixed in order to avoid leakage, we can only choose either 2-folds or 10-folds.
Although 10 folds is a common choice as it provides minmial information loss, we finally choose two folds for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two periods. It provides out-of-period stacking feature split by time, which is useful to avoid overfitting.

@@

\textbf{Fig. 1} shows the AUC perfomance of Local 5-folds Cross Validation result and 30\% of testing data using same parameters and seed.
 Although there's a difference in AUC between local CV and 30\% of testing data,
 there is a strong correlation on AUC between CV and testing data. The AUC improved when stacking is applied and result keep improving
 when more randomized stacking features is used.

\begin{figure}[ht!]
\centering
\includegraphics[width=125mm]{Rplot.png}
\caption{AUC of CV result and 30\% testing data using different number of stacking features. One standard deviation of the CV score is plotted via error bar. \label{overflow}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hyperparameters Optimization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We applied grid search on a subset of parameters. In general, $max\_depth$, $min\_child\_weight$, $gamma$, $lambda$ and $alpha$ are tuned for model complexity,
 $subsample$, $colsample\_bytree$ are tuned to avoid overfitting, $scale\_pos\_weight$ is used to re-balance dataset.
 In order to speed things up we used a high $eta$ (shrinkage) in the beginning and ranked parameter combinations based on cross validation score.
 For the parameter combinations with top 5\% ranking, we re-trained the model using a lower $eta$ and selected the one with best cross validation score.

For stacking we used random parameters without optimization
 because in practice stacking perform better when the underlying models are diversified.

@@

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{3cm}p{4cm}p{2cm}}
    \toprule
    Parameters & Description & Range of values & Final Choice \\
    \midrule
    $eta$ & Shrinkage in update & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of tree & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample of data & [0.7, 0.8, 0.9, 1] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

We only applied stacking on task 2 as task 1 is too compute-intensive.
We tried two stacking method seperately:
\begin{enumerate}
 \item 2-folds stacking split by two different time frame

@@

Since stacking index must be fixed in order to avoid leakage, we can only use either 2-folds or 10-folds stacking.
Although 10-folds is a common choice as it provides minimal information loss, we finally decided using 2-folds for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two periods. It provides out-of-period stacking feature split by time, which is useful to avoid overfitting.

@@

\textbf{Fig. 1} shows the AUC perfomance of Local 5-folds Cross Validation and 30\% of testing data using same parameters and seed.
 There is a strong correlation in AUC between Cross Validation and 30\% of testing data.
 The AUC improved once stacking is applied. We included more randomized stacking features until there is no improvement in AUC.

\begin{figure}[ht!]
\centering
\includegraphics[width=120mm]{Rplot.png}
\caption{AUC of CV result and 30\% testing data using different number of stacking features. One standard deviation of the CV score is plotted via error bar. \label{overflow}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hyperparameters Optimization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We applied grid search on a subset of parameters. In general, $max\_depth$, $min\_child\_weight$, $gamma$, $lambda$ and $alpha$ are tuned for model complexity,
 $subsample$, $colsample\_bytree$ are tuned to avoid overfitting, $scale\_pos\_weight$ is used to re-balance dataset.
 In order to speed things up we used a high $eta$ (shrinkage) in the beginning and ranked parameter combinations based on Cross Validation.
 For the parameter combinations with top 5\% ranking, we re-trained the model using a lower $eta$ and selected the one with best Cross Validation.

For stacking features we used random parameters without optimization
 because in practice stacking perform better when the underlying models are diversified.

@@

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{3cm}p{4cm}p{2cm}}
    \toprule
    Parameters & Description & Range of values & Final Choice \\
    \midrule
    $eta$ & Shrinkage & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of trees & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample of data & [0.7, 0.8, 0.9, 1] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}
